Adopting agile in the large: motivations, success factors and challenges

### 2013-10-28 journal/article.tex
Research method

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. The selection
of primary studies was done as a keyword based database search and manual
filtering of included studies. The filtering process was executed independently
by two researchers (Dikert, Paasivaara), and the process was audited by a third
external researcher (Lassenius). We deviated from Kitchenham's guideline in the
parts of study assessment and data extraction. These deviations are explained
below.

@@

>>>>

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. The selection
of primary studies was done as a keyword based database search and manual
filtering of included studies. The filtering process was executed independently
by two researchers (Dikert, Paasivaara), and the process was audited by a third
external researcher (Lassenius).

We deviated from Kitchenham's guideline in the parts of study assessment and
data extraction. These deviations are explained below.
--> This is maybe not true! The study assessment can also be done qualitatively.

Based on the research questions and intended focus of the research, we defined
an inclusion criteria with three facets: agile software engineering, focus on
transformation, and large organizations. The first facet covers primary studies
focusing on software engineering organizations applying or striving to apply
agile methods. Examples on topics excluded by the first facet are agile
manufacturing, and applying Scrum practices in management boards. The second
facet states that included studies must provide insights relevant to
organizational transformation, and specifically to the research questions.
The third facet underlines the particular contribution we aim to provide with
this research, namely the exclusive focus on large organizations.

--> Definition of large scale

--> Case studies ??

A database keyword search was chosen as the search strategy. Based on the
research questions three facets for keywords were chosen: agile software
development, organizational transformation, and large scale. Preliminary
searches showed however that picking keywords with good precision was very
difficult. As a result we excluded the third facet (large scale). Instead of
engineering the search terms, which proved to result in excluding some
relevant articles, we chose an approach of manually filtering the search
results. Still having a substantial part of the matches in the non-relevant  
areas such as agile manufacturing, we decided to limit searches to either be
included in major software publications or include the term ``software''. The
resulting facets and keywords are listed in Table \ref{table:searchterms}. The
databases included in the search are listed in Table \ref{table:databases}. All
databases supported searches using boolean search commands constructed from the
facets and keywords. The search yielded NNNN unique matches.

\begin{table}
    \begin{tabular}{ p{0.22\textwidth} p{0.76\textwidth} }
        \toprule
        Facet                  & Keywords   \\
        \midrule
        Agile methods\newline (before \& after) &
            agile, scrum, "extreme programming",\newline
            waterfall, "plan-driven", RUP \\
        Organizational transformation &
            transform*, transiti*, migrat*, journey, adopt*, deploy, introduc*,
            "roll-out", rollout \\
        Limit to software\newline related atricles &
            (software OR (conference="agile, xp, icgse, icse"))\newline
            NOT title+abs="manufacturing", conference="agile manufacturing"
        \\
        \bottomrule
    \end{tabular}
    \caption{Facets and related search terms used}
    \label{table:searchterms}
\end{table}

\begin{table}
    \begin{tabular}{ p{0.24\textwidth} l l }
        \toprule
        Database      & URL                     & N of matches   \\
        \midrule
        IEEExplore    & http://ieeexplore.ieee.org      & 745 \\ 
        ACM           & http://dl.acm.org               & 168 \\
        Scopus        & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge\newline(Thomson Reuters) &
        http://apps.webofknowledge.com & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search}
    \label{table:databases}
\end{table}

@@

The primary research for this literature review consists almost exclusively of
industry experience reports. This may be seen as a factor lessening the
evidence.
--> Why did we do this anyway?
--> Case studies with research method studying organizational transformations in
    software industry are very scarce.
--> Large organizational changes are hard to measure experimentally (controlled
    experiments?). Also due to this any student research was excluded.
